### 2016-09-30 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Final copy of hose stream report; minor edits to CAF and burner reports
Added manufacturer + device names to uncertainty section

\large
\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (May 2016) \\
% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
CODEN: NTNOEF }

@@

\subsubsection{Second Floor of West Structure}
The second floor of the West Structure was built on the structure's first floor wood ceiling support. The two floors were connected by an interior stairwell. A door made of lauan plywood was located at the top of the stairwell. The walls on the second floor were of wood-frame with 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers. Two layers of 16~mm (0.63~in) Type X gypsum board lined the interior side of the wood studs, and a layer of 13~mm (0.5~in) thick cement board covered the gypsum board. The interior ceiling of the second story was covered by two layers of 13~mm (0.5~in) thick cement board. The exterior side of the outer walls on the second floor were protected by 11~mm (0.44~in) thick OSB and 8~mm (0.31~in) fiber cement lap siding.

@@

\subsubsection{Thermocouples}
The standard uncertainty in the temperature of the thermocouple wire itself as determined by the wire manufacturer is $\pm$2.2$~^{\circ}$C at $277~^{\circ}$C and increases to $\pm$9.5$~^{\circ}$C at $871~^{\circ}$C~\cite{Omega:2004}. The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty. Expanded uncertainties as high as 20~\% for upper layer temperatures measured by a 1~mm bare-bead type K thermocouple have been reported by NIST researchers~\cite{Blevins:1999,Pitts:2003}. Small diameter thermocouples were used during these experiments to limit the impact of radiative heating and cooling. The estimated relative expanded uncertainty associated with the temperature measurements is $\pm$15~\%.

\subsubsection{Heat Flux Gauges}
Total heat flux measurements were made with water-cooled Schmidt-Boelter gauges. The manufacturer reports a $\pm$3~\% calibration expanded uncertainty for these devices~\cite{Medtherm:2003}. Results from an international study on total heat flux gauge calibration and response demonstrated that the relative expanded uncertainty of a Schmidt-Boelter gauge is typically $\pm$8~\%~\cite{Pitts:2006}.

\subsubsection{Gas Sampling}
The gas sampling system has a relative expanded uncertainty of $\pm$1~\% when compared with span gas volume fractions~\cite{Bundy:2007}. However, according to a study by Lock~et~al.~\cite{Lock:1}, the non-uniformity and movement of exhaust gases contribute to an estimated relative expanded uncertainty of $\pm$12~\%.

\subsubsection{Bi-Directional Probes}
Bi-directional probes were used to measure gas velocity in doorways. Bryant~\cite{Bryant:FSJ2009} estimates that the relative expanded uncertainty of this measurement ranges from $\pm$14~\% to $\pm$22~\%.

\subsubsection{Heat Release Rate}
A rotary type gas meter was used to measure the volume flow rate of propane into the gas burners. The manufacturer reports a relative standard uncertainty of $\pm$2~\%~\cite{Romet:2014}. A volumetric flow rate was calculated from the gas meter volume readings and used in conjunction with the heat of combustion of propane to calculate the heat release rate of the fire. The total expanded uncertainty for the heat release rate obtained from this method is estimated to be $\pm12$~\%.

>>>>

\large
\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (October 2016) \\
CODEN: NTNOEF }

@@

\subsubsection{Second Floor of West Structure}
The second floor of the West Structure was built on the structure's first floor wood ceiling support. The two floors were connected by an interior stairwell. A door made of lauan plywood was located at the top of the stairwell. The walls on the second floor were of wood-frame with 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers. Two layers of 16~mm (0.63~in) Type X gypsum board lined the interior side of the wood studs, and a layer of 13~mm (0.5~in) thick cement board covered the gypsum board. The interior ceiling of the second story was covered by two layers of 13~mm (0.5~in) thick cement board. The exterior sides of the outer walls on the second floor were protected by 11~mm (0.44~in) thick OSB and 8~mm (0.31~in) fiber cement lap siding.

@@

\subsubsection{Thermocouples}
The standard uncertainty in the temperature of the thermocouple wire itself as determined by the wire manufacturer, OMEGA Engineering, Inc., is $\pm$2.2$~^{\circ}$C at $277~^{\circ}$C and increases to $\pm$9.5$~^{\circ}$C at $871~^{\circ}$C~\cite{Omega:2004}. The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty. Expanded uncertainties as high as 20~\% for upper layer temperatures measured by a 1~mm bare-bead type K thermocouple have been reported by NIST researchers~\cite{Blevins:1999,Pitts:2003}. Small diameter thermocouples were used during these experiments to limit the impact of radiative heating and cooling. The estimated relative expanded uncertainty associated with the temperature measurements is $\pm$15~\%.

\subsubsection{Heat Flux Gauges}
Total heat flux measurements were made with water-cooled Schmidt-Boelter gauges. The manufacturer, MEDTHERM Corporation, reports a $\pm$3~\% calibration expanded uncertainty for these devices~\cite{Medtherm:2003}. Results from an international study on total heat flux gauge calibration and response demonstrated that the relative expanded uncertainty of a Schmidt-Boelter gauge is typically $\pm$8~\%~\cite{Pitts:2006}.

\subsubsection{Gas Sampling}
A gas sampling system with relative expanded uncertainty of $\pm$1~\% when compared to span gas volume fractions~\cite{Bundy:2007} from California Analytical Instruments, Inc. (model 602P) was used to make gas concentration measurements. However, according to a study by Lock~et~al.~\cite{Lock:1}, the non-uniformity and movement of exhaust gases contribute to an estimated relative expanded uncertainty of $\pm$12~\%.

\subsubsection{Bi-Directional Probes}
Bi-directional probes with Setra 264 pressure transducers from Setra Systems, Inc. were used to measure gas velocity in doorways. Bryant~\cite{Bryant:FSJ2009} estimates that the relative expanded uncertainty of this measurement ranges from $\pm$14~\% to $\pm$22~\%.

\subsubsection{Heat Release Rate}
A rotary type gas meter was used to measure the volume flow rate of propane into the gas burners. The manufacturer, Romet Limited, reports a relative standard uncertainty of $\pm$2~\%~\cite{Romet:2014} for this type of meter (model RM-3000). A volumetric flow rate was calculated from the gas meter volume readings and used in conjunction with the heat of combustion of propane to calculate the heat release rate of the fire. The total expanded uncertainty for the heat release rate obtained from this method is estimated to be $\pm8$~\%.
